Generating the Blueprints of the Java Ecosystem

### 2015-02-26 msr.tex
adding the import process

% dimitro@bkarak: say *WHY* these are important metrics. Say something like: "These metrics are important for developers and / or developers because [...]" Provide an example and a reference to show how they saved the universe.

In this paper we present: a) the construction process to
obtain the collection of the metrics results that the three aforementioned tools produced for {\bf (dimitro@bkarak: put the number of {\sc jar}s here)} {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.

% The rest of the paper is structured as follows; first, the dataset construction process is presented and analysed. Then we analyse the schema of the database. Along with the dataset limitations, we present examples and ideas of basic experimentation with the measurements.

@@

% Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis. These languages include Java, Clojure, Groovy, and Scala.

% dimitro@bkarak: *Major Concern*: You are not "selling" this right. These are bullets. You need to show that we put some effort to extract the results. Recall our previous data paper. You only mention the data cleaning part here. What happened when you got the JARs you wanted? You run the three tools? *How*? You need to show it. How did you automate this? The whole procedure. Something like the following: "Once we had the list with the project versions we run the above tools for 4000050 days by using a heavy metal script on one trillion machines."

The dataset construction process is illustrated in Figure~\cite{}.

\begin{figure}
\centering
\includegraphics[scale=0.5]{import-process}
\caption{}
\end{figure}

Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}. The Maven repository contains several versions of each project.

All versions were filtered out and only the latest was kept. For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code. Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 11,365 projects, with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.

@@

The descriptive names for each metric are stored in the \textit{measurement\_type} table.
% dimitro@bkarak: this is not the right way to reference tables. Which table is it? 5? 6? Same below.
There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them e.g. \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the {\sc clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the {\sc ckjm} tool.

>>>>

In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.

@@

Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis. These languages include Java, Clojure, Groovy, and Scala.

\begin{figure}
\centering
\includegraphics[scale=0.5]{import-process}
\caption{The dataset construction process}
\label{fig:dataset-construction}
\end{figure}

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}. The Maven repository contains several versions of each project. All versions were filtered out and only the latest was kept. Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code. The

Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 11,365 projects, with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.

@@

The descriptive names for each metric are stored in the \textit{measurement\_type} database table. There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them e.g. \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the {\sc clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the {\sc ckjm} tool.
